The problem and promise of scale in multilayer networks

### 2020-01-28 paper/manuscript.Rmd
add paper title to hab selection section
add acknowledge notes
edit abstract + intro

## Abstract
Scale remains a seminal concept in ecology. Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use. Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogeneous landscapes. Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics. Here, we test how multilayer network metrics (e.g., versatility, multi-degree, similarity) are sensitive to variation in an animal’s perception of scale. We will simulate animal movement data coupled with emergent social networks on increasingly heterogenous landscapes across spatial scales. Furthermore, we review specific examples of spatially explicit data types to include in multilayer networks and explore the relevant nuances of these data. *Our simulations will highlight the need to carefully select scales for measuring spatial processes and appropriately weight layers and edges representing different types of data.* Effective integration of spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate landscape ecology theory as a way to link different scales of social and spatial processes in a multilayer network. Based on social network and landscape ecology theory as well as our simulations we demonstrate potential for interconnectedness among individual animals and the landscapes they occupy.

@@

Here, we discuss and integrate variation in temporal and spatial scales within a multilayer network framework. We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a fission-fusion social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al. 2019). We use this case study to address two principal questions associated with scale-dependent multilayer networks. First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems? Second, can variation in spatial, temporal, and social scale improve predictions associated with seasonal differences in resource availability and social association? We conclude with perspectives for further development and application of scale in multilayer networks with respect to landscape ecology (Schneider 2009), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al. 2019).

@@

@@

>>>>

## Abstract
Scale remains a seminal concept in ecology. Spatial scale, for instance, has become a central consideration in the way we understand landscape ecology and animal space use. Meanwhile, social processes can also scale from fine-scale interactions to co-occurrence and overlapping home ranges. Multilayer networks promise the integration of monolayer animal social networks with the complexity and importance of animal movement and space use in heterogeneous landscapes. Despite the complex interplay between social networks and how animals use space, there remains an important biological and methodological gap in our understanding of an animal’s perception of spatial scale, e.g., grain and extent, can affect multilayer network dynamics. Here, we discuss the role of scale in the context of multilayer networks and provide a case study of caribou (*Rangifer tarandus*) to illustrate the role of social, spatial, temporal scale on multilayer processes. We also present perspectives on future development and application of scale in multilayer networks with respect to habitat selection and space use, individual fitness and phenotypes, and movement ecology and collective movement (Jolles et al. 2019).Effective integration of social and spatial processes, including biologically meaningful scales, within the context of animal social networks is an emerging area of research; our contribution will uniquely incorporate perspectives on how the social environment and spatial processes are linked across scales in a multilayer framework. Based on social network and behavioural ecology theory as well as our case study, we demonstrate potential for interconnectedness among individual animals, their social environment, and the landscapes they occupy.

@@

Here, we discuss and integrate variation in temporal and spatial scales within a multilayer network framework. We borrow from behavioural, landscape, and spatial ecology to build a conceptual and analytical framework for scale-dependent multilayer networks and we apply this framework to a fission-fusion social system case study of caribou (*Rangifer tarandus*) in Newfoundland, Canada (Peignier et al. 2019). We use this case study to address two principal questions associated with scale-dependent multilayer networks. First, to what degree does the spatial scale of landscapes, temporal windows of analysis, and social scale of relationships, influence our ability to interpret complex social systems? Second, can variation in social, spatial, and temporal scale improve predictions associated with seasonal differences in resource availability and social association? We conclude with perspectives for future development and application of scale in multilayer networks with respect to habitat selection and space use (Van Moorter et al. 2016), individual fitness and phenotypes (Webber & Vander Wal 2018), and movement ecology and collective movement (Jolles et al. 2019).

@@

Multi-scale habitat selection modeling: a review and outlook

@@

## Acknowledgements
* DCS
* check WG
